Bayesian Hierarchical Modeling: An Introduction and Reassessment

### 2022-08-19 manuscript.Rmd
Small updates

author: 
  - name          : "Myrthe Veenman"
    affiliation   : "2"
    corresponding : yes    # Define only one corresponding author
    address       : "Wassenaarseweg 52, Leiden"
    email         : "myrthe.veenman@gmail.com"
  - name          : "Angelika Stefan"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author
  - name          : "Julia Haaf"
    affiliation   : "1"
    corresponding : no    # Define only one corresponding author

affiliation:
  - id            : "1"
    institution   : "University of Amsterdam"
  - id            : "2"
    institution   : "Leiden University"

>>>>

author: 
  - name          : "Myrthe Veenman"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Wassenaarseweg 52, Leiden"
    email         : "myrthe.veenman@gmail.com"
  - name          : "Angelika Stefan"
    affiliation   : "2"
    corresponding : no    # Define only one corresponding author
  - name          : "Julia Haaf"
    affiliation   : "2"
    corresponding : no    # Define only one corresponding author

affiliation:
  - id            : "1"
    institution   : "Leiden University"
  - id            : "2"
    institution   : "University of Amsterdam"

### 2022-08-19 manuscript.tex
Small updates

  pdfauthor={Myrthe Veenman2, Angelika Stefan1, \& Julia Haaf1},

@@

\title{Bayesian Hierarchical Modeling: An Introduction and Reassessment}
\author{Myrthe Veenman\textsuperscript{2}, Angelika Stefan\textsuperscript{1}, \& Julia Haaf\textsuperscript{1}}
\date{}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} University of Amsterdam\\\textsuperscript{2} Leiden University}

>>>>

  pdfauthor={Myrthe Veenman1, Angelika Stefan2, \& Julia Haaf2},

@@

\title{Bayesian Hierarchical Modeling: An Introduction and Reassessment}
\author{Myrthe Veenman\textsuperscript{1}, Angelika Stefan\textsuperscript{2}, \& Julia Haaf\textsuperscript{2}}
\date{}

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} Leiden University\\\textsuperscript{2} University of Amsterdam}
